The \dealii{} Library, Version 9.2

### 2020-06-01 9.2/paper.tex
add date, leave a question

\dealii{} version 9.2.0 was released May XYZ, 2020.
\todo[inline]{Need to update date.}
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 9.2. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

The interface is now as simple to use as the one for $h$-adaptive mesh refinement.
Consider the following (incomplete) listing as an example: We estimate both error and
smoothness of the finite element approximation. Further, we flag certain fractions of
cells with the highest and lowest errors for refinement and coarsening, respectively
(here: 30\%/3\%). From those cells listed for adaptation, we designate a subset
for $h$- and $p$-adaptation (here: 10\%/90\%). The parameters of the corresponding
\texttt{hp::Refinement} function specify the fraction of cells to be $p$-adapted from
those subsets flagged for refinement and coarsening, respectively.
\begin{c++}
Vector<float> estimated_error_per_cell(n_active_cells);
KellyErrorEstimator::estimate(
dof_handler, ..., solution, estimated_error_per_cell, ...);
GridRefinement::refine_and_coarsen_fixed_number(
triangulation, estimated_error_per_cell, 0.3, 0.03);

>>>>

\dealii{} version 9.2.0 was released May 20, 2020.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 9.2. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

The interface is now as simple to use as the one for $h$-adaptive mesh refinement.
Consider the following (incomplete) listing as an example: We estimate both error and
smoothness of the finite element approximation. Further, we flag certain fractions of
cells with the highest and lowest errors for refinement and coarsening, respectively
(here: 30\%/3\%). From those cells listed for adaptation, we designate a subset
for $h$- and $p$-adaptation (here: 10\%/90\%).
\todo[inline]{Timo asks: is this a typo in the code where you say 0.9, 0.9?}
The parameters of the corresponding
\texttt{hp::Refinement} function specify the fraction of cells to be $p$-adapted from
those subsets flagged for refinement and coarsening, respectively.
\begin{c++}
Vector<float> estimated_error_per_cell(n_active_cells);
KellyErrorEstimator::estimate(
dof_handler, ..., solution, estimated_error_per_cell, ...);
GridRefinement::refine_and_coarsen_fixed_number(
triangulation, estimated_error_per_cell, 0.3, 0.03);
